---
title       : WhichUni Web App
author      : Alex Spiers
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## WhichUni: English and Welsh University Stats Web Application

- WhichUni is a shiny web application that is an interactive visualisation of publicly available information
from HESA (Higher Education Statistics Agency)

- WhichUni allows users to view English and Welsh univerisities after filtering by the entry requirements of students (UCAS points)

- Author: Alex Spiers

---

## WhichUni: Data Set

```{r echo=FALSE}
setwd("C:/Users/Alex/Google Drive/Personal/COURSERA/9.Developing Data Products/DevDataProdProject")
instStats <- readRDS("instStats.rda")
```

- UNISTATS Dataset is a publicly available information set collected by the Higher Education Statistics Agency in the UK

- The data set can be found on the [HESA website] (https://www.hesa.ac.uk/unistatsdata)

- The data set includes the following variables:
  - *Unversity Name*
  - *tariffMean* this is the mean number of UCAS points (post-16 qualifications)
  that students have on entry to their course at University.
  - *instPremMean* this is a measure of the "Salary Premium" obtained by graduates from the
  university. This is calculated as a percentage increase/decrease when compared to graduates
  studying the same course nationally.
  - *totalUpper* the percentage of students that have obtained a first or upper-second degree.
  - *Location* the location of the campus.
  
---



## WhichUni: Features - Bubble Map

Users can choose to display the data as a ```googleVis``` package "Bubble"" Map 

```{r echo=FALSE}
library(googleVis)
library(dplyr)
setwd("C:/Users/Alex/Google Drive/Personal/COURSERA/9.Developing Data Products/DevDataProdProject")
## Prepare data to be displayed
instStats <- readRDS("instStats.rda")
```

```{r results = 'asis', echo=FALSE}
options(gvis.plot.tag='chart')
library(googleVis)
Bubble <- gvisBubbleChart(instStats, idvar="NAME", 
                          xvar="tariffMean", yvar="instPremMean",
                          sizevar="totalFirst",
                          options=list(
                            width=1200,height=800,
                            hAxis='{minValue:75, maxValue:125}'))
plot(Bubble)
```

---

## WhichUni: Features - Bubble Map

Users can choose to display the data as a ```googleVis``` package "Bubble" Chart or "GeoMap"

```{r echo=FALSE}
library(googleVis)
library(dplyr)
setwd("C:/Users/Alex/Google Drive/Personal/COURSERA/9.Developing Data Products/DevDataProdProject")
instStats <- readRDS("instStats.rda")
## Prepare data to be displayed
```

```{r results = 'asis', message = F, echo = F}
options(gvis.plot.tag='chart')
library(googleVis)
Bubble <- gvisBubbleChart(instStats, idvar="NAME", 
                          xvar="tariffMean", yvar="instPremMean",
                          sizevar="totalFirst",
                          options=list(
                            width=800,height=400,
                            hAxis='{minValue:75, maxValue:125}'))
plot(Bubble)
```

---

## WhichUni: Intended User Base

Intended users include:

- Prospective students: can use the web app to inform their choices before applying to university

- Employers and graduate recruiters: can use web app to identify key talent for their recruitment

- University Marketing deparments: can use web app to benchmark their institutions against the competition and highlight unique aspects.

